Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli

### 2024-11-10 manuscript_draft.Rmd
update draft with bimodal

title       : "Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning with Multiple Stimuli"

@@

1)  How do pilot data influence sample size suggestions?

>>>>

title       : "Accuracy in Parameter Estimation and Simulation Approaches for Sample Size Planning Accounting for Item Effects"

@@

1)  How does pilot data influence sample size suggestions?
